### 2021-01-08 rscripts/manuscript-results.Rmd
adjust figures size

---
title: "Different populations agree on which moral arguments underlie which opinions"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      dpi = 300, dev="jpeg", out.width = "40%", 
                      fig.align = "center",
                      tidy = TRUE)

library(readr)
library(dplyr)
library(tidyr)
library(purrr)
library(forcats)
library(ggplot2)
library(DescTools)
library(kableExtra)
library(cowplot)

theme_set(theme_half_open(11))

```

```{r data, echo=FALSE}

# US

us_arg <- read_csv("../data/us-argument-data-clean.csv")

us_arg <- us_arg %>% 
  mutate(
    age_gr = cut(age, 
                 breaks = c(0, median(age, na.rm = TRUE), 100), 
                 labels = c("Younger", "Older")),
    verb_ability = ifelse(wordsum > median(wordsum, na.rm = TRUE),
                          "Higher",
                          "Lower"),
    edu = fct_collapse(edu, 
                       Lower = "<bach", 
                       Higher = c("bach", "grad")),
   position = paste0(issue, "_", type)
  )

# UK

uk_arg <- read_csv("../data/uk-argument-data-clean.csv")

uk_arg <- uk_arg %>% 
  mutate(
    age_gr = cut(age, 
                 breaks = c(0, median(age, na.rm = TRUE), 100), 
                 labels = c("Younger", "Older")),
    polviews = cut(polviews_10, 
                   breaks = c(0, 3, 6, 10),
                   include.lowest = TRUE,
                   labels = c("Left", "Moderate", "Right")),
       position = paste0(issue, "_", type)
  )

# Israel

il_arg <- read_csv("../data/il-argument-data-clean.csv")
il_arg <- il_arg %>% 
  mutate(
    age_gr = cut(age, 
                 breaks = c(0, median(age, na.rm = TRUE), 100), 
                 labels = c("Younger", "Older")),
    polviews = cut(polviews_10, 
                   breaks = c(0, 3, 6, 10),
                   include.lowest = TRUE,
                   labels = c("Left", "Moderate", "Right")),
    edu = ifelse(edu > 4, "Higher", "Lower"),
    position = paste0(issue, "_", type)
  )

# Brazil

br_arg <- read_csv("../data/br-argument-data-clean.csv")
br_arg <- br_arg %>% 
  mutate(
    age_gr = cut(age, 
                 breaks = c(0, median(age, na.rm = TRUE), 100), 
                 labels = c("Younger", "Older")),
    polviews = cut(polviews_10, 
                   breaks = c(0, 3, 6, 10),
                   include.lowest = TRUE,
                   labels = c("Left", "Moderate", "Right")),
    edu = ifelse(edu > 4, "Higher", "Lower"),
    position = paste0(issue, "_", type)
  )

# Combined dataset
common_items <- read_csv("../data/gss-and-bsa-common-items.csv")

comb_arg <- bind_rows(
  us_arg %>% 
    filter(issue %in% common_items$gss_code) %>% 
    mutate(sample = "US"), 
  uk_arg %>% 
    filter(issue %in% common_items$bsa_code) %>% 
    # use GSS variable code for issue to unify between US and UK samples
    rename(bsa_code = issue) %>% 
    left_join(common_items %>% 
                select(issue = gss_code, bsa_code, reverse)) %>% 
    # one BSA item is reversed
    mutate(
      type = case_when(
        reverse == 1 & type == "pro" ~ "against", 
        reverse == 1 & type == "against" ~ "pro",
        TRUE ~ type
      ), 
      position = paste0(issue, "_", type),
      sample = "UK") %>% 
    select(-bsa_code, -reverse), 
  il_arg %>% 
    mutate(sample = "IL"), 
  br_arg %>% 
    mutate(sample = "BR")
)

```

```{r functions, echo=FALSE}

# estimate argument applicability within separate groups defined by group_var

link_by_group <- function(data, group_var) {

group_var <- enquo(group_var)

arg_link_by_group <- data %>% 
    drop_na(!!group_var) %>% 
    mutate(group = fct_relabel(!!group_var,
                               ~as.character(as.numeric(as.factor(.))))) %>%
    group_by(mf, position, group) %>% 
    summarise(link = mean(value)) %>% 
    spread(group, link)

arg_link_by_group %>% 
  drop_na() %>% 
  mutate(group = as_label(group_var))
}

# estimate CCC between argument applicability measures in the groups defined by group_var

ccc_by_group <- function(data, group_var) {
  group_var <- enquo(group_var)

  arg_link_by_group <- data %>% 
    drop_na(!!group_var) %>% 
    mutate(group = fct_relabel(!!group_var, ~as.character(as.numeric(as.factor(.))))) %>% 
    group_by(mf, position, group) %>% 
    summarise(link = mean(value), .groups = "drop") %>% 
    spread(group, link)

  arg_link_by_group %>% 
    drop_na() %>% 
    summarise(CCC(`2`, `1`)$rho.c,
              .groups = "drop") %>% 
    mutate(group = as_label(group_var))
}

```

# Study 1. US

## Method

```{r us_sample}

us_sample <- us_arg %>% 
  select(id, age, sex, polviews, edu, verb_ability, issue) %>% 
  distinct() %>% 
  group_by(id, age, sex, polviews, edu, verb_ability) %>% 
  summarise(n_issues = n()) %>% 
  ungroup()

us_sample %>% 
  summarise(n = n(),
            mean(n_issues),
            women = mean(sex == "female", na.rm = TRUE),
            mean_age = mean(age, na.rm = TRUE),
            sd_age = sd(age, na.rm = TRUE),
            liberal = mean(polviews == "liberal", na.rm = TRUE),
            conservative = mean(polviews == "conservative", na.rm = TRUE), 
            verb_higher = mean(verb_ability == "Higher"), 
            edu_higher = mean(edu == "Higher"))

```

## Results

```{r us_boxpl, fig.width=7, fig.height=5, fig.cap = "Figure 1. Boxplots showing how applicability, estimated in the entire sample of Study 1, of eight different kinds of moral arguments varied across 196 moral opinions. The box represents the interquartile (IQ) range with the dark line indicating the median. The whiskers reach the min and max values in case these are at most 1.5 times the box height outside the IQ range. Circles and stars signify outliers (values between 1.5 and 3 times the IQ range) and extreme outliers (more than 3 times the IQ range), respectively."}

us_arg_connection  <- us_arg %>% 
  group_by(mf, position) %>% 
  summarise(link = mean(value))

us_arg_connection <- us_arg_connection %>% 
  mutate(iqr = IQR(link), 
         lower = quantile(link, .25), 
         higher = quantile(link, .75),
         outl_type = case_when(
          link < lower - 3*iqr ~ 8, 
          link > higher + 3*iqr ~ 8,
          link < lower - 1.5*iqr ~ 1, 
          link > higher + 1.5*iqr ~ 1
          ))

us_arg_connection %>% 
  ggplot(aes(mf, link)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(aes(shape = outl_type), size = 1.5, stroke = .5) +
  scale_shape_identity() +
  theme(legend.position = "none") +
  labs(y = "Arguments applicablity", x = "Moral foundation")

#ggsave("fig1_us-arg-applicability.jpeg", width = 180, height = 80, units = "mm", dpi = 300)

```

```{r us_rand_ccc, cache = TRUE}

# Simulate 100 random splits in two even groups and calculate the mean CCC
set.seed(8404)
us_rand_gr_mult <- tibble(id = rep(unique(us_arg$id), 100),
                       draw = rep(1:100, 
                                    each = length(unique(us_arg$id)))) %>%
  mutate(rand_gr = rbinom(n = n(), size = 1, prob = .5),
         rand_gr = factor(rand_gr))

us_ccc_rand_gr <- left_join(us_arg, us_rand_gr_mult) %>%
  group_by(draw, mf, position, rand_gr) %>%
  summarise(link = mean(value)) %>%
  spread(rand_gr, link) %>% 
  group_by(draw) %>%
  summarise(DescTools::CCC(`0`, `1`)$rho.c,
            r = cor(`0`, `1`, use = "pair")) %>% 
  summarise(rand_gr = mean(est))

```

```{r us_ccc}

us_mf_agreement <- bind_rows(
  ccc_by_group(us_arg, polviews),
  ccc_by_group(us_arg, sex),
  ccc_by_group(us_arg, age_gr),
  ccc_by_group(us_arg, verb_ability),
  ccc_by_group(us_arg, edu)
)

us_mf_agreement <- us_mf_agreement %>% 
  mutate(label = sprintf("%.2f [%.2f, %.2f]", est, lwr.ci, upr.ci), 
         group = factor(group,
                        levels = c("sex", 
                                   "age_gr",
                                   "polviews", 
                                   "edu",
                                   "verb_ability"), 
                        labels = c("Sex", 
                                   "Age", 
                                   "Ideology", 
                                   "Education",
                                   "Verbal ability"))) %>% 
  arrange(group)

us_mf_agreement %>%  
  select(group, label) %>% 
  kbl(col.names = c(" ", "CCC with 95% CI"),
      caption = "Table 2. CCC values with 95% confidence interval.") %>% 
  kable_classic(full_width = FALSE)

```

```{r fig.height=3.9, fig.cap="Figure 2. Scatter plots of 1,568 argument applicability scores (8 types of arguments by 196 moral opinions), measured in different groups in the United States: women vs. men (A),  younger vs. older (B), liberals vs. conservatives (C), higher vs. lower education (D), and higher vs. lower verbal ability (E). Regression lines in blue and reference lines for perfect agreement in black."}

us_mf_link_by_gr <- bind_rows(
  link_by_group(us_arg, polviews),
  link_by_group(us_arg, sex),
  link_by_group(us_arg, age_gr),
  link_by_group(us_arg, verb_ability),
  link_by_group(us_arg, edu)
)

scatter_plot <- function(data) {

  data %>% 
    ggplot(aes(`1`, `2`)) +
    geom_point(alpha = .2) +
    geom_abline() +
    geom_smooth(method = "lm", se = FALSE) +
    scale_x_continuous(limits = c(0, 1), 
                       breaks = c(0, .25, .50, .75, 1))+ 
    scale_y_continuous(limits = c(0, 1), 
                       breaks = c(0, .25, .5, .75, 1)) +
    theme(axis.text = element_text(size = 9),
          plot.margin = margin(t = 1, r = 5, b = 1, l = 5))
}

pl1 <-  us_mf_link_by_gr %>% 
  filter(group == "sex") %>% 
  scatter_plot() +
  labs(x = "Women", y = "Men") +
  theme(strip.background = element_blank(), strip.text = element_blank())

pl2 <-  us_mf_link_by_gr %>% 
  filter(group == "age_gr") %>% 
  scatter_plot() +
  labs(x = "Younger", y = "Older")+
  theme(strip.background = element_blank(), strip.text = element_blank())

pl3 <- us_mf_link_by_gr %>% 
  filter(group == "polviews") %>% 
  scatter_plot() +
  labs(x = "Liberals", y = "Conservatives")

pl4 <- us_mf_link_by_gr %>% 
  filter(group == "edu") %>% 
  scatter_plot() +
  labs(x = "Lower education", y = "Higher education")+
  theme(strip.background = element_blank(), strip.text = element_blank())

pl5 <-  us_mf_link_by_gr %>% 
  filter(group == "verb_ability") %>% 
  scatter_plot() +
  labs(x = "Higher verbal ability", y = "Lower\nverbal ability")+
  theme(strip.background = element_blank(), strip.text = element_blank())

cowplot::plot_grid(pl1, pl2, pl3, pl4, pl5, 
                   labels = "AUTO", 
                   label_size = 11)

# ggsave("fig2_us-scatter-by-groups.jpeg", width = 180, height = 100, 
#        units = "mm", dpi = 300)

```

# Study 2. UK

## Method

```{r uk_sample}

uk_sample <- uk_arg %>% 
  select(polviews, id, issue, age, sex, edu) %>% 
  distinct() %>% 
  group_by(polviews, id, age, sex, edu) %>% 
  summarise(n_issues = n(), .groups = "drop")

uk_sample %>% 
  summarise(n = n(),
            mean(n_issues),
            women = mean(sex == "Female", na.rm = TRUE),
            mean_age = mean(age, na.rm = TRUE),
            sd_age = sd(age, na.rm = TRUE),
            left = mean(polviews == "Left", na.rm = TRUE),
            moderate = mean(polviews == "Moderate", na.rm = TRUE),
            right = mean(polviews == "Right", na.rm = TRUE),
            edu_higher = mean(edu == "higher", na.rm = TRUE))

```

## Results

```{r uk_boxpl, fig.height=3.1, fig.cap = "Figure 3. Boxplots (defined in Figure 2) showing how applicability, estimated in the entire sample of Study 2, of eight different kinds of moral arguments varied across 216 moral opinions."}

uk_arg_connection  <- uk_arg %>% 
  group_by(mf, position) %>% 
  summarise(link = mean(value))

uk_arg_connection <- uk_arg_connection %>% 
  mutate(iqr = IQR(link), 
         lower = quantile(link, .25), 
         higher = quantile(link, .75),
         outl_type = case_when(
          link < lower - 3*iqr ~ 8, 
          link > higher + 3*iqr ~ 8,
          link < lower - 1.5*iqr ~ 1, 
          link > higher + 1.5*iqr ~ 1
          ))

uk_arg_connection %>% 
  ggplot(aes(mf, link)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(aes(shape = outl_type), size = 1.5, stroke = .5) +
  scale_shape_identity() +
  theme(legend.position = "none") +
  labs(y = "Arguments applicablity", x = "Moral foundation")

# ggsave("fig3_uk-arg-applicability.jpeg", width = 180, height = 80, units = "mm", dpi = 300)

```

```{r uk_rand_ccc, cache = TRUE}

# Simulate 100 random splits in two even groups and calculate the mean CCC
set.seed(8405)
uk_rand_gr_mult <- tibble(id = rep(unique(uk_arg$id), 100),
                       draw = rep(1:100, 
                                    each = length(unique(uk_arg$id)))) %>%
  mutate(rand_gr = rbinom(n = n(), size = 1, prob = .5),
         rand_gr = factor(rand_gr))

uk_ccc_rand_gr <- left_join(uk_arg, uk_rand_gr_mult) %>%
  group_by(draw, mf, position, rand_gr) %>%
  summarise(link = mean(value)) %>%
  spread(rand_gr, link) %>% 
  group_by(draw) %>%
  summarise(DescTools::CCC(`0`, `1`)$rho.c,
            r = cor(`0`, `1`, use = "pair")) %>% 
  summarise(rand_gr = mean(est))

```

```{r uk_ccc}

uk_mf_agreement <- bind_rows(
  ccc_by_group(filter(uk_arg, 
                      polviews %in% c("Left", "Right")) %>% 
                 droplevels(), 
               polviews),
  ccc_by_group(uk_arg, sex),
  ccc_by_group(uk_arg, age_gr),
  ccc_by_group(uk_arg, edu)
)

uk_mf_agreement <- uk_mf_agreement %>% 
  mutate(label = sprintf("%.2f [%.2f, %.2f]", est, lwr.ci, upr.ci), 
         group = factor(group,
                        levels = c("sex", 
                                   "age_gr",
                                   "polviews", 
                                   "edu"), 
                        labels = c("Sex", 
                                   "Age", 
                                   "Ideology", 
                                   "Education"))) %>% 
  arrange(group)

uk_mf_agreement %>%  
  select(group, label) %>% 
  kbl(col.names = c(" ", "CCC with 95% CI")) %>% 
  kable_classic(full_width = FALSE)

```

```{r fig.width=3.3, fig.height=2.7}

uk_mf_diff <- bind_rows(
  link_by_group(filter(uk_arg, polviews %in% c("Left", "Right")) %>%
                  droplevels(), 
                polviews),
  link_by_group(uk_arg, sex),
  link_by_group(uk_arg, age_gr),
  link_by_group(uk_arg, edu)
)

scatter_plot <- function(data) {

  data %>% 
    ggplot(aes(`1`, `2`)) +
    geom_point(alpha = .2) +
    geom_abline() +
    geom_smooth(method = "lm", se = FALSE) +
    scale_x_continuous(limits = c(0, 1), 
                       breaks = c(0, .25, .50, .75, 1)) + 
    scale_y_continuous(limits = c(0, 1), breaks = c(0, .25, .5, .75, 1)) +
    theme_half_open(9) 
}

pl1 <-  uk_mf_diff %>% 
  filter(group == "sex") %>% 
  scatter_plot() +
  labs(x = "Women", y = "Men") +
  theme(strip.background = element_blank(), strip.text = element_blank())

pl2 <-  uk_mf_diff %>% 
  filter(group == "age_gr") %>% 
  scatter_plot() +
  labs(x = "Younger", y = "Older")+
  theme(strip.background = element_blank(), strip.text = element_blank())

pl3 <- uk_mf_diff %>% 
  filter(group == "polviews") %>% 
  scatter_plot() +
  labs(x = "Left-wing", y = "Right-wing")

pl4 <- uk_mf_diff %>% 
  filter(group == "edu") %>% 
  scatter_plot() +
  labs(x = "Lower education", y = "Higher education")+
  theme(axis.title.y = element_text(size = 8))

cowplot::plot_grid(pl1, pl2, pl3, pl4,
                   labels = "AUTO", 
                   label_size = 9)

# ggsave("fig4_uk-scatter-by-groups.jpeg", width = 85, height = 70, units = "mm", dpi = 300)

```

# Study 3. Combined US, UK, IL, and BR analysis

## Method

```{r common_items}

common_items %>% 
  mutate(bsa_text = ifelse(reverse == 1, 
                           paste0(bsa_text, "*"),
                           bsa_text)) %>% 
  select(gss_text, bsa_text) %>% 
  kbl(col.names = c("General Social Survey items",
                    "British Social Attitudes items"),
      caption = "Table 4. Matching items identified in the GSS and BSA. An asterisk (*) indicates that the issue positions were reverse coded in the UK version to match the US version.") %>% 
    kable_classic()

```

### IL sample

```{r il_sample}

il_sample <- il_arg %>% 
  select(id, issue, age, sex, polviews) %>% 
  distinct() %>% 
  group_by(id, age, sex, polviews) %>% 
  summarise(n_issues = n()) %>% 
  ungroup()

il_sample %>% 
  summarise(n = n(),
            mean(n_issues),
            women = mean(sex == "Female", na.rm = TRUE),
            mean_age = mean(age, na.rm = TRUE),
            sd_age = sd(age, na.rm = TRUE),
            left = mean(polviews == "Left", na.rm = TRUE),
            moderate = mean(polviews == "Moderate", na.rm = TRUE),
            right = mean(polviews == "Right", na.rm = TRUE))

```

### BR sample

```{r br_sample}

br_sample <- br_arg %>% 
  select(id, issue, age, sex, polviews) %>% 
  distinct() %>% 
  group_by(id, age, sex, polviews) %>% 
  summarise(n_issues = n()) %>% 
  ungroup()

br_sample %>% 
  summarise(n = n(),
            mean(n_issues),
            women = mean(sex == "Female", na.rm = TRUE),
            mean_age = mean(age, na.rm = TRUE),
            sd_age = sd(age, na.rm = TRUE),
            left = mean(polviews == "Left", na.rm = TRUE),
            moderate = mean(polviews == "Moderate", na.rm = TRUE),
            right = mean(polviews == "Right", na.rm = TRUE))

```

## Results

```{r com_scatter, fig.width = 4.7, fig.cap="Figure 5. Scatter plots of 432 argument applicability scores for (8 types of arguments by 54 moral opinions). Each row compares data from two of our four countries US, UK, Israel (IL) and Brazil (BR). Every plot includes the CCC value with 95% confidence interval. Regression lines in blue and reference lines for perfect agreement in black."}

improve_plot <- function(pl, label_data) {
  ccc_label <- sprintf("%.2f [%.2f, %.2f]", 
                       label_data$est, 
                       label_data$lwr.ci, 
                       label_data$upr.ci)

  pl +
    geom_point(alpha = .4) +
    geom_abline() +
    geom_smooth(method = "lm", se = FALSE) +
    annotate(geom = "text", label = ccc_label,
             x = 0, y = .95, hjust = 0, size = 3.3) +
    scale_x_continuous(limits = c(0, 1), 
                       breaks = c(0, .25, .50, .75, 1)) + 
    scale_y_continuous(limits = c(0, 1), 
                       breaks = c(0, .25, .5, .75, 1)) +
    theme(axis.text = element_text(size = 9),
          plot.margin = margin(t = 1, r = 5, b = 1, l = 5), 
          strip.text = element_text(size = 12))
}

arg_link_by_group <- comb_arg %>%
  group_by(mf, position, sample) %>%
  summarise(link = mean(value), .groups = "drop") %>%
  spread(sample, link)

us_uk_pl <- arg_link_by_group %>% 
  ggplot(aes(US, UK)) %>% 
  improve_plot(label_data = summarise(arg_link_by_group, 
                                      CCC(US, UK)$rho.c)) + 
  labs(x = "US sample", y = "UK sample")

us_il_pl <- arg_link_by_group %>% 
  ggplot(aes(US, IL)) %>% 
  improve_plot(label_data = summarise(arg_link_by_group, 
                                      CCC(US, IL)$rho.c)) + 
  labs(x = "US sample", y = "IL sample")

us_br_pl <- arg_link_by_group %>% 
  ggplot(aes(US, BR)) %>% 
  improve_plot(label_data = summarise(arg_link_by_group, 
                                      CCC(US, BR)$rho.c)) + 
  labs(x = "US sample", y = "BR sample")

uk_il_pl <- arg_link_by_group %>% 
  ggplot(aes(UK, IL)) %>% 
  improve_plot(label_data = summarise(arg_link_by_group, 
                                      CCC(UK, IL)$rho.c)) + 
  labs(x = "UK sample", y = "IL sample")

uk_br_pl <- arg_link_by_group %>% 
  ggplot(aes(UK, BR)) %>% 
  improve_plot(label_data = summarise(arg_link_by_group, 
                                      CCC(UK, BR)$rho.c)) + 
  labs(x = "UK sample", y = "BR sample")

il_br_pl <- arg_link_by_group %>% 
  ggplot(aes(IL, BR)) %>% 
  improve_plot(label_data = summarise(arg_link_by_group, 
                                      CCC(IL, BR)$rho.c)) + 
  labs(x = "IL sample", y = "BB sample")

cowplot::plot_grid(us_uk_pl, NULL, NULL,
                   us_il_pl, uk_il_pl, NULL,
                   us_br_pl, uk_br_pl, il_br_pl)

# ggsave("fig5_scatter-by-cntry.jpeg", width = 180, height = 120, 
#        units = "mm", dpi = 300)

```

## Agreement on argument applicability

```{r agr_ccc, cache = TRUE}

comb_arg_full <- bind_rows(
  comb_arg %>% 
    filter(sample %in% c("IL", "BR")),
  us_arg %>%  mutate(sample = "US"),
  uk_arg %>% mutate(sample = "UK") 
)

# Probability to agree for each issue
  p_agree <- comb_arg_full %>%
    filter(type == "pro") %>%
    select(sample, id, issue, opinion) %>%
    distinct() %>%
    group_by(sample, issue) %>%
    mutate(p = mean(opinion)) %>% 
    select(-opinion)

estimate_random_ccc <- function(data) {

  # Draw random opinion for each issue and espimated p
  rand_opin_simulated <- data %>% 
    mutate(pro = rbinom(n = n(), size = 1, prob = p),
           against = 1 - pro) %>%
    gather("type", "rand_opinion", pro, against)

  # Join argument data and calculate CCC
  left_join(rand_opin_simulated, 
            comb_arg_full %>% 
              select(sample, id, issue, mf, value),
            by = c("sample", "id", "issue")) %>% 
    group_by(sample, mf, issue, type, rand_opinion) %>%
    summarise(link = mean(value), .groups = "drop") %>%
    spread(rand_opinion, link) %>%
    drop_na() %>%
    group_by(sample) %>%
    summarise(est = CCC(`0`, `1`)$rho.c$est, .groups = "drop") 
}

set.seed(28943)

# Make 100 ccc simulations and average 
random_ccc <- map_df(1:100, ~estimate_random_ccc(p_agree)) %>% 
  group_by(sample) %>% 
  summarise(exp_ccc = mean(est))

ccc_for_agreement <- comb_arg_full %>% 
  group_by(sample, mf, issue, position, opinion) %>% 
  summarise(link = mean(value), .groups = "drop") %>% 
  spread(opinion, link) %>% 
  drop_na() %>% 
  group_by(sample) %>% 
  summarise(n_opinin = n_distinct(position), CCC(`0`, `1`)$rho.c) %>% 
  transmute(sample, 
            n_opinin, 
            ccc = sprintf("%.2f [%.2f, %.2f]", est, lwr.ci, upr.ci))

left_join(ccc_for_agreement, random_ccc) %>%
  mutate(sample = fct_rev(sample),
         exp_ccc = sprintf("%.2f", exp_ccc)) %>% 
  arrange(sample) %>% 
  kbl(col.names = c(
    "Country", 
    "Number of opinions",
    "CCC with 95% CI",
    "Expected CCC under perfect agreement"
    )) %>% 
  kable_classic(full_width = FALSE)

```

### 2021-02-16 rscripts/supplementary-material.Rmd
add supplementary material

---
title: "Different populations agree on which moral arguments underlie which opinions"
subtitle: "Supplementary Material"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      dpi = 300, dev="jpeg", fig.width = 180/25.4,
                      tidy = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(forcats)
library(purrr)
library(kableExtra)
library(ggplot2)
library(broom)

theme_set(cowplot::theme_cowplot(10))

gss_items <- read_csv("../data/gss-items.csv") 
bsa_items <- read_csv("../data/bsa-items.csv") 
common_items <- read_csv("../data/gss-and-bsa-common-items.csv")

us_arg <- read_csv("../data/us-argument-data-clean.csv")

us_arg <- us_arg %>% 
  mutate(
    sex = fct_relevel(sex, "male"),
    age_gr = cut(age, 
                 breaks = c(0, median(age, na.rm = TRUE), 100), 
                 labels = c("Younger", "Older")),
    verb_ability = ifelse(wordsum > median(wordsum, na.rm = TRUE),
                          "Higher",
                          "Lower"),
    verb_ability = fct_relevel(verb_ability, "Lower"),
    edu = fct_collapse(edu, 
                       Lower = "<bach", 
                       Higher = c("bach", "grad")),
   position = paste0(issue, "_", type),
   mf = factor(mf, levels = c("Harm", "Fairness", "Liberty", "Violence",
                            "Authority", "Purity", "Ingroup", "Government"))
  )

uk_arg <- read_csv("../data/uk-argument-data-clean.csv")

uk_arg <- uk_arg %>% 
  mutate(
    age_gr = cut(age, 
                 breaks = c(0, median(age, na.rm = TRUE), 100), 
                 labels = c("Younger", "Older")),
    polviews = cut(polviews_10, 
                   breaks = c(0, 3, 6, 10),
                   include.lowest = TRUE,
                   labels = c("Left", "Moderate", "Right")),
    position = paste0(issue, "_", type)
  )

```

## Supplementary Tables

**Supplementary Table 1.** The list of 98 GSS moral items.

```{r table1}

gss_items %>% 
  kbl() %>% 
    kable_classic()

```

**Supplementary Table 2.** The list of 108 BSA moral items.

```{r table2}

bsa_items %>% 
  kbl() %>% 
    kable_classic()

```

**Supplementary Table 3.** Matching items identified in the GSS and BSA. An asterisk (*) indicates that the issue positions were reverse coded in the UK version to match the US version.

```{r table3}

common_items %>% 
  mutate(bsa_text = ifelse(reverse == 1, 
                           paste0(bsa_text, "*"),
                           bsa_text)) %>% 
  select(gss_text, bsa_text) %>% 
  kbl(col.names = c("General Social Survey items",
                    "British Social Attitudes items")) %>% 
    kable_classic()

```

## Supplementary Analysis

In this section, we use logistic regression to explore the marginal effects of individual characteristics controlling for rater’s own opinion as well their interactions. Supporting main analysis, the results show that strong effects of individual characteristics are rare and mostly within what would be expected by chance (see Supplementary Figures 1-4. While we present the results for interaction only between ideology and sex, similar results were obtained for interaction between ideology and other individual characteristics).

## Supplementary Figures

```{r glm_mod, cache = TRUE}

by_pos_mf <- us_arg %>% 
  group_by(position, mf) %>% 
  nest()

fit_glm <- function(data) {
  glm(value ~ sex + age_gr + polviews + edu + verb_ability + opinion, 
      family = binomial(),
      data)
}

by_pos_mf <- by_pos_mf %>% 
  mutate(mod = map(data, possibly(fit_glm, NULL)))

by_pos_mf <- by_pos_mf %>% 
  mutate(mod_sex_int = map2(mod, data, ~possibly(update, NULL)(.x, data = .y, . ~ . + sex:polviews)),
         mod_opin_int = map2(mod, data, ~possibly(update, NULL)(.x, data = .y, . ~ . + opinion:polviews)))

```

```{r fig1, fig.width=180/25.4, fig.asp=0.7, fig.cap="Supplementary Figure 1. Distributions of Z-scores for the effect of sex, age, ideology, education, verbal ability, and agreement with the opinion on the probability to find each of the eight kinds of argument applicable to each of the 196 GSS opinions in the US sample. For comparison, the black line shows the standard normal distribution. The vertical grey lines separate coefficients that are above or below zero by at least two standard errors. Note: The y-axis scale is cut at 0.5 for better visibility. The zero effect can spike up until 2 for violence applicability."}

glm_coef <- by_pos_mf %>% 
  mutate(coef = map(mod, tidy)) %>% 
  select(-data, -mod) %>% 
  unnest(coef)

glm_coef %>% 
  filter(term != "(Intercept)") %>% 
  mutate(term = factor(term, 
                       levels = unique(term),
                       labels = c("Female", "Older", "Liberal",
                                  "Higher\neducation",
                                  "Higher\nverb. ab.", 
                                  "Agree"))) %>%
  ggplot(aes(statistic)) +
  geom_histogram(aes(y = after_stat(density))) +
  geom_vline(xintercept = c(-2, 2), color = "grey50") +
  stat_function(fun = dnorm,  
                args = list(mean = 0, sd = 1)) +
  facet_grid(term ~ mf) +
  coord_cartesian(ylim = c(0, .5), xlim = c(-3.5, 3.5))+
  scale_y_continuous(breaks = c(0, .2, .4)) +
  xlab("z-score")

```

```{r fig2, fig.width=180/25.4, fig.asp=0.8, fig.cap="Supplementary Figure 2. The same as Suplementarty Figure 1, but also inculdes estimates of the interaction between gender and ideology."}

glm_coef_sex_int <- by_pos_mf %>% 
  mutate(coef = map(mod_sex_int, tidy)) %>% 
  select(-data, -mod) %>% 
  unnest(coef)

glm_coef_sex_int %>% 
  filter(term != "(Intercept)") %>% 
  mutate(term = factor(term, 
                       levels = unique(term),
                       labels = c("Female", "Older", "Liberal",
                                  "Higher\neducation",
                                  "Higher\nverb. ab.",
                                  "Agree",
                                  "Female x\nLiberal"))) %>%
  ggplot(aes(statistic)) +
  geom_histogram(aes(y = after_stat(density))) +
  geom_vline(xintercept = c(-2, 2), color = "grey50") +
  stat_function(fun = dnorm,  
                args = list(mean = 0, sd = 1)) +
  facet_grid(term~mf) +
  coord_cartesian(ylim = c(0, .5), xlim = c(-3.5, 3.5))+
  scale_y_continuous(breaks = c(0, .2, .4)) + 
  xlab("z-score")

```

```{r fig3, eval = FALSE, fig.width=180/25.4, fig.asp=0.8, fig.cap="Supplementary Figure 2"}

glm_coef_opin_int <- by_pos_mf %>% 
  mutate(coef = map(mod_opin_int, tidy)) %>% 
  select(-data, -mod) %>% 
  unnest(coef)

glm_coef_opin_int %>% 
  filter(term != "(Intercept)") %>% 
  mutate(term = factor(term, 
                       levels = unique(term),
                       labels = c("Female", "Older", "Liberal",
                                  "Higher\neducation",
                                  "Higher\nverb. ab.", 
                                  "Agree",
                                  "Agree x\nLiberal"))) %>%
  ggplot(aes(statistic)) +
  geom_histogram(aes(y = after_stat(density))) +
  geom_vline(xintercept = c(-2, 2), color = "grey50") +
  stat_function(fun = dnorm,  
                args = list(mean = 0, sd = 1)) +
  facet_grid(term~mf) +
  coord_cartesian(ylim = c(0, .5), xlim = c(-3.5, 3.5)) +
  scale_y_continuous(breaks = c(0, .2, .4)) +   xlab("z-score")

```

```{r fig4, eval=FALSE, fig.width=180/25.4, fig.asp=0.8, fig.cap="Supplementary Figure 2"}

glm_coef_verb_int <- by_pos_mf %>% 
  mutate(coef = map(mod_verb_int, tidy)) %>% 
  select(-data, -mod) %>% 
  unnest(coef)

glm_coef_verb_int %>% 
  filter(term != "(Intercept)") %>% 
  mutate(term = factor(term, 
                       levels = unique(term),
                       labels = c("Female", "Older", "Liberal",
                                  "Higher\neducation",
                                  "Higher\nverb. ab.", 
                                  "Higher\nverb.ab.x\nLiberal"))) %>%
  ggplot(aes(statistic)) +
  geom_histogram(aes(y = after_stat(density))) +
  geom_vline(xintercept = c(-2, 2), color = "grey50") +
  stat_function(fun = dnorm,  
                args = list(mean = 0, sd = 1)) +
  facet_grid(term~mf) +
  coord_cartesian(ylim = c(0, .5), xlim = c(-3.5, 3.5))+
  scale_y_continuous(breaks = c(0, .2, .4)) +   xlab("z-score")

```

```{r uk_mod, cache = TRUE}

uk_by_pos_mf <- uk_arg %>% 
  mutate(polviews = fct_rev(polviews),
         sex = fct_relevel(sex, "Male")) %>% 
  group_by(position, mf) %>% 
  nest()

fit_glm <- function(data) {
  glm(value ~ sex + age_gr + polviews + edu + opinion,
      family = binomial(),
      data)
}

uk_by_pos_mf <- uk_by_pos_mf %>% 
  mutate(mod = map(data, possibly(fit_glm, NULL)))

uk_by_pos_mf <- uk_by_pos_mf %>% 
  mutate(mod_sex_int = map2(mod, data, ~possibly(update, NULL)(.x, data = .y, . ~ . + sex:polviews)),
         mod_opin_int = map2(mod, data, ~possibly(update, NULL)(.x, data = .y, . ~ . + opinion:polviews)))

```

```{r fig5, fig.width=180/25.4, fig.asp=0.6, fig.cap="Supplementary Figure 3. Distributions of Z-scores for the effect of sex, age, ideology, education, and agreement with the opinion on the probability to find each of the eight kinds of argument applicable to each of the 216 BSA opinions in the UK sample. For comparison, the black line shows the standard normal distribution. The vertical grey lines separate coefficients that are above or below zero by at least two standard errors. Note: The y-axis scale is cut at 0.5 for better visibility. The zero effect can spike up until 2 for violence applicability."}

uk_by_pos_mf <- uk_by_pos_mf  %>% 
  ungroup() %>% 
  mutate(mf = factor(mf, levels = c("Harm", "Fairness", "Liberty", "Violence",
                            "Authority", "Purity", "Ingroup", "Government")))

glm_coef <- uk_by_pos_mf %>% 
  mutate(coef = map(mod, tidy)) %>% 
  select(-data, -mod) %>% 
  unnest(coef)

glm_coef %>% 
  filter(term != "(Intercept)") %>% 
  mutate(term = factor(term, 
                       levels = unique(term),
                       labels = c("Female", "Older", "Moderate", "Left",
                                  "Higher\neducation", "Agree"))) %>%
  ggplot(aes(statistic)) +
  geom_histogram(aes(y = after_stat(density))) +
  geom_vline(xintercept = c(-2, 2), color = "grey50") +
  stat_function(fun = dnorm,  
                args = list(mean = 0, sd = 1)) +
  facet_grid(term~mf) +
  coord_cartesian(ylim = c(0, .5), xlim = c(-3.5, 3.5))+
  scale_y_continuous(breaks = c(0, .2, .4)) +   xlab("z-score")

```

```{r fig6, fig.width=180/25.4, fig.asp=0.8, fig.cap="Supplementary Figure 4. The same as Suplementarty Figure 3, but also inculdes estimates of the interaction between gender and ideology. "}

glm_coef_sex_int <- uk_by_pos_mf %>% 
  mutate(coef = map(mod_sex_int, tidy)) %>% 
  select(-data, -mod) %>% 
  unnest(coef)

glm_coef_sex_int %>% 
  filter(term != "(Intercept)") %>% 
  mutate(term = factor(term, 
                       levels = unique(term),
                       labels = c("Female", "Older", "Moderate", "Left",
                                  "Higher\neducation", "Agree",
                                  "Female x\nModerate", "Female x\nLeft"))) %>%
  ggplot(aes(statistic)) +
  geom_histogram(aes(y = after_stat(density))) +
  geom_vline(xintercept = c(-2, 2), color = "grey50") +
  stat_function(fun = dnorm,  
                args = list(mean = 0, sd = 1)) +
  facet_grid(term~mf) +
  coord_cartesian(ylim = c(0, .5), xlim = c(-3.5, 3.5))+
  scale_y_continuous(breaks = c(0, .2, .4)) +   xlab("z-score")

```

```{r fig7, eval = FALSE, fig.width=180/25.4, fig.asp=0.8, fig.cap="Supplementary Figure 2"}

glm_coef_opin_int <- uk_by_pos_mf %>% 
  mutate(coef = map(mod_opin_int, tidy)) %>% 
  select(-data, -mod) %>% 
  unnest(coef)

glm_coef_opin_int %>% 
  filter(term != "(Intercept)") %>% 
  mutate(term = factor(term, 
                       levels = unique(term),
                       labels = c("Female", "Older", "Moderate", "Left",
                                  "Higher\neducation", "Agree",
                                  "Agree x\nModerate", "Agree x\nLeft"))) %>%
  ggplot(aes(statistic)) +
  geom_histogram(aes(y = after_stat(density))) +
  geom_vline(xintercept = c(-2, 2), color = "grey50") +
  stat_function(fun = dnorm,  
                args = list(mean = 0, sd = 1)) +
  facet_grid(term~mf) +
  coord_cartesian(ylim = c(0, .5), xlim = c(-3.5, 3.5)) +
  scale_y_continuous(breaks = c(0, .2, .4)) +   xlab("z-score")

```

### 2021-02-16 rscripts/manuscript-results.Rmd
adjust figures size
update results
update results with revision

@@
 
-knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
-                      dpi = 300, dev="jpeg", out.width = "40%", 
-                      fig.align = "center",
-                      tidy = TRUE)
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
+                      fig.width = 7.1, fig.height = 3.15,
+                      dpi = 300, dev="jpeg", tidy = TRUE)
 
@@
 
-```{r data, echo=FALSE}
+```{r data}
 
@@
   mutate(
+    sex = fct_relevel(sex, "male"),
     age_gr = cut(age, 
@@
                           "Lower"),
+    verb_ability = fct_relevel(verb_ability, "Lower"),
     edu = fct_collapse(edu, 
@@
                        Higher = c("bach", "grad")),
-   position = paste0(issue, "_", type)
+   position = paste0(issue, "_", type),
+   mf = factor(mf, levels = c("Harm", "Fairness", "Liberty", "Violence",
+                            "Authority", "Purity", "Ingroup", "Government"))
   )
@@
                    labels = c("Left", "Moderate", "Right")),
-       position = paste0(issue, "_", type)
+    edu = factor(edu, levels = c("lower", "higher"), labels = c("Lower", "Higher")),
+    position = paste0(issue, "_", type),
+   mf = factor(mf, levels = c("Harm", "Fairness", "Liberty", "Violence",
+                            "Authority", "Purity", "Ingroup", "Government"))
   )
@@
 # Israel
+il_arg <- read_csv("../data/il-argument-data-clean.csv")
 
-il_arg <- read_csv("../data/il-argument-data-clean.csv")
 il_arg <- il_arg %>% 
@@
 # Brazil
-
 br_arg <- read_csv("../data/br-argument-data-clean.csv")
@@
 
-```{r functions, echo=FALSE}
+```{r functions}
 
@@
 
+get_group_prop <- function(data, group_var) {
+  group_var <- enquo(group_var)
+
+  data %>% 
+    drop_na(!!group_var) %>% 
+    summarise(prop = mean(!!group_var == first(!!group_var))) %>% 
+    mutate(group = as_label(group_var))
+}
+
+estimate_random_group_ccc <- function(data, p = .5) {
+
+  data %>% 
+    # draw random group
+    mutate(rand_gr = rbinom(n = n(), size = 1, prob = p),
+           rand_gr = factor(rand_gr)) %>% 
+    # aggregate arg connection by random group
+    group_by(mf, position, rand_gr) %>%
+    summarise(link = mean(value), .groups = "drop") %>%
+    # calculate CCC
+    spread(rand_gr, link) %>% 
+    summarise(ccc = DescTools::CCC(`0`, `1`)$rho.c$est) %>% 
+    pull(ccc)
+}
+
 ```
@@
 
-```{r us_boxpl, fig.width=7, fig.height=5, fig.cap = "Figure 1.
+```{r us_boxpl, fig.cap = "Figure 1.
 Boxplots showing how applicability, estimated in the entire sample of Study 1, of eight different kinds of moral arguments varied across 196 moral opinions.
@@
 
-#ggsave("fig1_us-arg-applicability.jpeg", width = 180, height = 80, units = "mm", dpi = 300)
+# ggsave("fig1_us-arg-applicability.jpeg", width = 180, height = 80, units = "mm", dpi = 300)
 
@@
 
-```{r us_rand_ccc, cache = TRUE}
-
-# Simulate 100 random splits in two even groups and calculate the mean CCC
-set.seed(8404)
-us_rand_gr_mult <- tibble(id = rep(unique(us_arg$id), 100),
-                       draw = rep(1:100, 
-                                    each = length(unique(us_arg$id)))) %>%
-  mutate(rand_gr = rbinom(n = n(), size = 1, prob = .5),
-         rand_gr = factor(rand_gr))
-
-us_ccc_rand_gr <- left_join(us_arg, us_rand_gr_mult) %>%
-  group_by(draw, mf, position, rand_gr) %>%
-  summarise(link = mean(value)) %>%
-  spread(rand_gr, link) %>% 
-  group_by(draw) %>%
-  summarise(DescTools::CCC(`0`, `1`)$rho.c,
-            r = cor(`0`, `1`, use = "pair")) %>% 
-  summarise(rand_gr = mean(est))
-
-```
-
-```{r us_ccc}
+```{r us_ccc, cache = TRUE}
 
@@
 
+us_group_p <- bind_rows(
+  get_group_prop(us_arg, polviews),
+  get_group_prop(us_arg, sex),
+  get_group_prop(us_arg, age_gr),
+  get_group_prop(us_arg, verb_ability),
+  get_group_prop(us_arg, edu)
+)
+
+set.seed(28943)
+
+us_mf_agreement <- left_join(us_mf_agreement, us_group_p)
+
+make_1000_draws <- function(prop) {
+  map_dbl(1:1000, ~estimate_random_group_ccc(us_arg, prop))
+}
+
 us_mf_agreement <- us_mf_agreement %>% 
+  mutate(rand_ccc = map(prop, make_1000_draws))
+
+us_mf_agreement <- us_mf_agreement %>% 
+  mutate(p = map2_dbl(est, rand_ccc, ~mean(.y < .x)),
+         mean_rand = map_dbl(rand_ccc, mean))
+
+us_mf_agr_table <- us_mf_agreement %>% 
   mutate(label = sprintf("%.2f [%.2f, %.2f]", est, lwr.ci, upr.ci),
+         p = sprintf("%.3f", p), 
          group = factor(group,
@@
                                    "Verbal ability"))) %>% 
+  select(group, label, mean_rand, p) %>% 
   arrange(group)
 
-us_mf_agreement %>%  
-  select(group, label) %>% 
-  kbl(col.names = c(" ", "CCC with 95% CI"),
-      caption = "Table 2. CCC values with 95% confidence interval.") %>% 
+us_mf_agr_table %>%  
+  kbl(col.names = c("Compared subsamples", 
+                    "CCC with 95% CI", 
+                    "Expected CCC based on random split", 
+                    "p"),
+      caption = "Table 2. CCC values with 95% confidence interval.",
+      digits = 3) %>% 
   kable_classic(full_width = FALSE)
@@
 
-```{r fig.height=3.9, fig.cap="Figure 2.
+```{r fig.height=3.94, fig.cap="Figure 2.
 Scatter plots of 1,568 argument applicability scores (8 types of arguments by 196 moral opinions), measured in different groups in the United States: women vs.
@@
 
+Variance ratio between higher and lower verbal ability.
+
+```{r}
+
+us_mf_link_by_gr %>% 
+  filter(group == "verb_ability") %>% 
+  rename(higher = `1`, lower = `2`) %>% 
+  group_by(mf) %>%
+  summarise_at(vars(higher, lower), var) %>% 
+  transmute(mf, ratio = lower/higher) %>% 
+  arrange(ratio)
+
+```
+
 # Study 2. UK
@@
 uk_sample %>% 
-  summarise(n = n(),
+  summarise(n = n_distinct(id),
             mean(n_issues),
@@
             right = mean(polviews == "Right", na.rm = TRUE),
-            edu_higher = mean(edu == "higher", na.rm = TRUE))
+            edu_higher = mean(edu == "Higher", na.rm = TRUE))
 
@@
 
-```{r uk_boxpl, fig.height=3.1, fig.cap = "Figure 3.
+```{r uk_boxpl, fig.cap = "Figure 3.
 Boxplots (defined in Figure 2) showing how applicability, estimated in the entire sample of Study 2, of eight different kinds of moral arguments varied across 216 moral opinions."}
@@
 
-```{r uk_rand_ccc, cache = TRUE}
-
-# Simulate 100 random splits in two even groups and calculate the mean CCC
-set.seed(8405)
-uk_rand_gr_mult <- tibble(id = rep(unique(uk_arg$id), 100),
-                       draw = rep(1:100, 
-                                    each = length(unique(uk_arg$id)))) %>%
-  mutate(rand_gr = rbinom(n = n(), size = 1, prob = .5),
-         rand_gr = factor(rand_gr))
-
-uk_ccc_rand_gr <- left_join(uk_arg, uk_rand_gr_mult) %>%
-  group_by(draw, mf, position, rand_gr) %>%
-  summarise(link = mean(value)) %>%
-  spread(rand_gr, link) %>% 
-  group_by(draw) %>%
-  summarise(DescTools::CCC(`0`, `1`)$rho.c,
-            r = cor(`0`, `1`, use = "pair")) %>% 
-  summarise(rand_gr = mean(est))
-
-```
-
-```{r uk_ccc}
+```{r uk_ccc, cache = TRUE}
 
@@
 
+uk_group_prop <- bind_rows(
+  get_group_prop(filter(uk_arg, 
+                      polviews %in% c("Left", "Right")) %>% 
+                 droplevels(), polviews),
+  get_group_prop(uk_arg, sex),
+  get_group_prop(uk_arg, age_gr),
+  get_group_prop(uk_arg, edu)
+)
+
+set.seed(653452)
+
+uk_mf_agreement <- left_join(uk_mf_agreement, uk_group_prop)
+
+make_1000_draws <- function(data, prop) {
+  map_dbl(1:1000, ~estimate_random_group_ccc(data, prop))
+}
+
+uk_mf_agreement$data <- list(
+   droplevels(filter(uk_arg, polviews %in% c("Left", "Right"))),
+   uk_arg,
+   uk_arg,
+   uk_arg
+)
+
 uk_mf_agreement <- uk_mf_agreement %>% 
+  mutate(rand_ccc = map2(data, prop, make_1000_draws))
+
+uk_mf_agreement <- uk_mf_agreement %>% 
+  mutate(p = map2_dbl(est, rand_ccc, ~mean(.y < .x)),
+         mean_rand = map_dbl(rand_ccc, mean))
+
+uk_mf_agr_table <- uk_mf_agreement %>% 
   mutate(label = sprintf("%.2f [%.2f, %.2f]", est, lwr.ci, upr.ci), 
@@
                                    "Ideology", 
-                                   "Education"))) %>% 
+                                   "Education")),
+         p = sprintf("%.3f", p)) %>% 
+  select(group, label, mean_rand, p) %>% 
   arrange(group)
 
-uk_mf_agreement %>%  
-  select(group, label) %>% 
-  kbl(col.names = c(" ", "CCC with 95% CI")) %>% 
+uk_mf_agr_table %>%  
+  kbl(col.names = c("Compared subsamples", 
+                    "CCC with 95% CI", 
+                    "Expected CCC based on random split", 
+                    "p"),
+      digits = 3,
+      caption = "Table 3. The CCC value with 95% confidence interval.") %>% 
   kable_classic(full_width = FALSE)
@@
 
-```{r fig.width=3.3, fig.height=2.7}
+```{r fig.width=3.35, fig.height=2.76, fig.cap="Figure 4.
+Scatter plots of 1,728 argument applicability scores (8 types of arguments by 216 moral opinions), measured in different groups in the United Kingdom: women vs.
+men (A),  younger vs.
+older (B), right-wing vs.
+left-wing (C), and higher vs.
+lower education (D).
+Regression lines in blue and reference lines for perfect agreement in black."}
 
@@
 
-```{r common_items}
-
-common_items %>% 
-  mutate(bsa_text = ifelse(reverse == 1, 
-                           paste0(bsa_text, "*"),
-                           bsa_text)) %>% 
-  select(gss_text, bsa_text) %>% 
-  kbl(col.names = c("General Social Survey items",
-                    "British Social Attitudes items"),
-      caption = "Table 4. Matching items identified in the GSS and BSA. An asterisk (*) indicates that the issue positions were reverse coded in the UK version to match the US version.") %>% 
-    kable_classic()
-
-```
-
 ### IL sample
@@
 
-```{r com_scatter, fig.width = 4.7, fig.cap="Figure 5.
+```{r ccc_bw_cntry, cache = TRUE}
+
+comp_table <- tibble(combination = combn(unique(comb_arg$sample), 2, simplify = FALSE))
+
+add_ccc_prop_for_comb <- function(combination) {
+  df <- comb_arg %>% 
+    filter(sample %in% combination)
+
+  bind_cols(
+    ccc_by_group(df, sample) %>% select(-group),
+    get_group_prop(df, sample) %>% select(-group)
+    )
+}
+
+comp_table <- comp_table %>% 
+  mutate(label = map_chr(combination, paste0, collapse = " "),
+         map_df(combination, add_ccc_prop_for_comb))
+
+set.seed(83045)
+
+make_1000_draws <- function(data, prop) {
+  map_dbl(1:1000, ~estimate_random_group_ccc(data, prop))
+}
+
+comp_table <- comp_table %>% 
+  mutate(rand_ccc = map2(combination, prop, 
+                         ~make_1000_draws(filter(comb_arg, sample %in% .x), .y)))
+
+comp_table <- comp_table %>% 
+  mutate(p = map2_dbl(est, rand_ccc, ~mean(.y < .x)),
+         mean_rand = map_dbl(rand_ccc, mean))
+
+comp_table_format <- comp_table %>% 
+  mutate(ccc = sprintf("%.2f [%.2f, %.2f]", est, lwr.ci, upr.ci),
+         p = sprintf("%.3f", p)) %>% 
+  select(label, ccc, mean_rand, p)
+
+comp_table_format %>%  
+  kbl(col.names = c("Compared subsamples", 
+                    "CCC with 95% CI", 
+                    "Expected CCC based on random split", 
+                    "p"),
+      digits = 3,
+      caption = "Table 4. The CCC value with 95% confidence interval.") %>% 
+  kable_classic(full_width = FALSE)
+
+```
+
+```{r com_scatter, fig.height = 4.7, fig.cap="Figure 5.
 Scatter plots of 432 argument applicability scores for (8 types of arguments by 54 moral opinions).
 Each row compares data from two of our four countries US, UK, Israel (IL) and Brazil (BR).
-Every plot includes the CCC value with 95% confidence interval.
 Regression lines in blue and reference lines for perfect agreement in black."}
@@
 improve_plot <- function(pl, label_data) {
-  ccc_label <- sprintf("%.2f [%.2f, %.2f]", 
-                       label_data$est, 
-                       label_data$lwr.ci, 
-                       label_data$upr.ci)
 
@@
     geom_smooth(method = "lm", se = FALSE) +
-    annotate(geom = "text", label = ccc_label,
-             x = 0, y = .95, hjust = 0, size = 3.3) +
     scale_x_continuous(limits = c(0, 1), 
@@
                                       CCC(IL, BR)$rho.c)) + 
-  labs(x = "IL sample", y = "BB sample")
+  labs(x = "IL sample", y = "BR sample")
 
@@
 # Make 100 ccc simulations and average 
-random_ccc <- map_df(1:100, ~estimate_random_ccc(p_agree)) %>% 
-  group_by(sample) %>% 
-  summarise(exp_ccc = mean(est))
+random_ccc <- map_df(1:1000, ~estimate_random_ccc(p_agree))
+
+random_ccc_by_sample <- random_ccc %>% 
+  chop(est) %>% 
+  rename(rand_ccc = est)
 
@@
   group_by(sample) %>% 
-  summarise(n_opinin = n_distinct(position), CCC(`0`, `1`)$rho.c) %>% 
-  transmute(sample, 
-            n_opinin, 
-            ccc = sprintf("%.2f [%.2f, %.2f]", est, lwr.ci, upr.ci))
+  summarise(n_opinin = n_distinct(position), CCC(`0`, `1`)$rho.c)
 
-left_join(ccc_for_agreement, random_ccc) %>%
-  mutate(sample = fct_rev(sample),
-         exp_ccc = sprintf("%.2f", exp_ccc)) %>% 
+ccc_for_agreement <- left_join(ccc_for_agreement, random_ccc_by_sample)
+
+ccc_for_agreement <- ccc_for_agreement %>% 
+  mutate(p = map2_dbl(est, rand_ccc, ~mean(.y < .x)),
+         mean_rand = map_dbl(rand_ccc, mean),
+         median_rand = map_dbl(rand_ccc, median))
+
+ccc_for_agr_tbl <- ccc_for_agreement %>% 
+  mutate(ccc = sprintf("%.2f [%.2f, %.2f]", est, lwr.ci, upr.ci), 
+         sample = fct_rev(sample),
+         mean_rand = sprintf("%.3f", mean_rand)) %>% 
+  select(sample, n_opinin, ccc, mean_rand, p)
+
+ccc_for_agr_tbl %>% 
   arrange(sample) %>% 
@@
     "CCC with 95% CI",
-    "Expected CCC under perfect agreement"
-    )) %>% 
+    "Expected CCC under perfect agreement",
+    "p"
+    ),
+    caption = "Table 5.
+CCC values, with 95% confidence intervals, measuring in four countries the extent to which people with different opinions on the underlying moral issues agreed on argument applicability.") %>%
   kable_classic(full_width = FALSE)

### 2021-02-16 rscripts/manuscript-results.Rmd
reduce out.width

@@
                       fig.width = 7.1, fig.height = 3.15, 
+                      out.width = "60%", fig.align = 'center',
                       dpi = 300, dev="jpeg", tidy = TRUE)
@@
 
-```{r fig.width=3.35, fig.height=2.76, fig.cap="Figure 4.
+```{r fig.width=3.35, fig.height=2.76, out.width = "40%", fig.cap="Figure 4.
 Scatter plots of 1,728 argument applicability scores (8 types of arguments by 216 moral opinions), measured in different groups in the United Kingdom: women vs.

### 2021-03-03 rscripts/manuscript-results.Rmd
accepted version

@@
 
-# ggsave("fig1_us-arg-applicability.jpeg", width = 180, height = 80, units = "mm", dpi = 300)
+# ggsave("fig1_us-arg-applicability.eps", 
+#        width = 180, height = 80, units = "mm")
 
@@
 
-# ggsave("fig2_us-scatter-by-groups.jpeg", width = 180, height = 100,
-#        units = "mm", dpi = 300)
+# ggsave("fig2_us-scatter-by-groups.eps", pl,
+#        device = cairo_ps, fallback_resolution = 600,
+#        width = 180, height = 100,
+#        units = "mm")
 
@@
 
-# ggsave("fig3_uk-arg-applicability.jpeg", width = 180, height = 80, units = "mm", dpi = 300)
+# ggsave("fig3_uk-arg-applicability.eps", width = 180, height = 80, units = "mm")
 
@@
 
-# ggsave("fig4_uk-scatter-by-groups.jpeg", width = 85, height = 70, units = "mm", dpi = 300)
+# ggsave("fig4_uk-scatter-by-groups.eps", pl,
+#        device = cairo_ps, fallback_resolution = 600,
+#        width = 120, height = 100, units = "mm")
 
@@
 
-# ggsave("fig5_scatter-by-cntry.jpeg", width = 180, height = 120,
-#        units = "mm", dpi = 300)
-
+# ggsave("fig5_scatter-by-cntry.eps", 
+#        device = cairo_ps, fallback_resolution = 600,
+#        width = 180, height = 120,
+#         units = "mm")
 ```
@@
 
-set.seed(28943)
+# The results in the manuscript are negligibly different due to using a different seed value
+
+set.seed(653452)
 
